Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-02 neurips-20/cvx-flats.tex

\bo{Rewrote this, Mon Jun 1 a.m.}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
We consider two kinds of consistency.
In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
Here we will define $L$ to be consistent (Definition \ref{def:consistent-prop}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
In the second, we are given a \textbf{target loss} $\ell$ and we define $L$ to be consistent (Definition \ref{def:consistent-ell}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.

>>>>

%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to
\raft{I like this phrasing -- nicely captures all settings}
solving the target problem of interest.
We consider two kinds of consistency.
In the first, we are given a \emph{target loss} $\ell$ and we define $L$ to be consistent (Definition \ref{def:consistent-ell}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.
In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
Here we will define $L$ to be consistent (Definition \ref{def:consistent-prop}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
